\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-07-21 paper/paper.tex
Play around with some plots, minor edits in intro

\newpage
\tableofcontents
\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
Consumers have an interest in accurate assessment of product reliability. Toward this end, there is a need for models that fit the data together with methods that account for uncertainty.  While computationally convenient, simple lifetime models can fail to capture key characteristics found in real data.

@@

The GLFP model has a meaningful parameterization and accommodates lifetime data with infant mortality and wearout.  Unfortunately, it can require a lot of data to fit due to the model's complexity.  Bayesian methods offer a means of reducing the amount of data required to estimate the model by leveraging multiple sources of information. When multiple populations are of interest, comparisons based on separate, unrestricted GLFP model fits will be limited to those products with sufficient data. As we will show, hierarchical modeling of the GLFP parameters allows for borrowing of information across populations which imposes "soft" constraints on model parameters. This enables estimation of the lifetime distribution for all populations via shrinkage toward a "pooled" model, with the degree of shrinkage inversely related to the amount of population specific information. We demonstrate computation of various quantities of interest while comparing reliability across populations using numerical integration over the posterior distribution with samples obtained via  Markov Chain Monte Carlo.

>>>>

\newpage
\tableofcontents
\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
Consumers have an interest in accurate assessment of product reliability. Toward this end, there is a need for models that reflect observable facts "on the ground", and methods which can make the most of available data and properly account for uncertainty.
%While computationally convenient, simple lifetime models can fail at each of these.

@@

The GLFP model has a meaningful parameterization and accommodates lifetime data with infant mortality and wearout.  Unfortunately, it can require a lot of data to fit due to the model's complexity. When multiple sources of information are available, partial pooling via hierarchical modeling is a way to reduce the amount of data required to produce stable estimates of the model parameters. When multiple populations are of interest, comparisons based on separate, unrestricted GLFP model fits will be limited to those products with sufficient data. As we will show, hierarchical modeling of the GLFP parameters allows for borrowing of information across populations which imposes "soft" constraints on model parameters. This enables estimation of the lifetime distribution for all populations via shrinkage toward a "pooled" model, with the degree of shrinkage inversely related to the amount of population specific information. We demonstrate computation of various quantities of interest while comparing reliability across populations using numerical integration over the posterior distribution with samples obtained via  Markov Chain Monte Carlo.
